PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-17 paper/sec-results.tex
added description of mg5amc

In this section we demonstrate the capabilities of \textsc{mg5\_aMC}+\textsc{PineAPPL} by
computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
for a representative set of processes in which EW corrections may have a
sizeable effect on the accuracy of the theoretical predictions.
In order to consider some realistic kinematics for these
processes, we rely on a set of measurements that are commonly included in PDF
fits. Our aim is twofold. First, we want to validate the results
obtained with \textsc{PineAPPL}; second, we want to assess the
impact of the EW corrections for the specific experimental setups. We describe
the settings employed for the computations, and the corresponding results for
each process.

>>>>

In this section we demonstrate the capabilities of \textsc{mg5\_aMC}+\textsc{PineAPPL} by
computing fast-interpolation grids, accurate to NLO QCD and NLO QCD+EW,
for a representative set of processes in which EW corrections may have a
sizeable effect on the accuracy of the theoretical predictions.
In order to consider some realistic kinematics for these
processes, we rely on a set of measurements that are commonly included in PDF
fits. Our aim is twofold. First, we want to validate the results
obtained with \textsc{PineAPPL}; second, we want to assess the
impact of the EW corrections for the specific experimental setups. We describe
the settings employed for the computations, and the corresponding results for
each process. We remind the reader that \textsc{mg5\_aMC} makes it possible
to compute predictions including NLO QCD and EW corrections for arbitrary processes
in an automated manner. It employs the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np}
as automated in \textsc{MadFKS}~\cite{Frederix:2009yq,Frederix:2016rdc} to deal with IR singularities. One-loop
amplitudes are computed by \textsc{MadLoop}~\cite{Hirschi:2011pa}, which employs different
numerical techniques~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn,Ossola:2006us,Cascioli:2011va,Mastrolia:2012bu} implemented in the corresponding computer libraries~\cite{Ossola:2007ax,Peraro:2014cba,Hirschi:2016mdz,Denner:2016kdg}. Matching
with parton showers is available only for pure-QCD corrections via the MC@NLO method~\cite{Frixione:2002ik}, and 
will not be employed in the following.
